---
title: "PrindleRd_HydroCAD"
author: "Adrian Wiegman"
date: "8/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message= FALSE)
dependancies <- c("tidyverse",
                  "zoo", # time series functions
                  "broom", # applying functions to nested data
                  "evapotranspiration", # evapotranspiration modeling
                  "lubridate", # easy date formatting
                  "forecast", # time series functions
                  "cowplot", # to make nice figure pannels
                  "patchwork", # to make nice figure pannels
                  "scales", # to access break formatting functions
                  "akima", # for interpolation of matrixes
                  "rgl") # for plotting 3d matrixes
lapply(dependancies,require,character.only=T)
```

```{r}
require(stringr)
# Load data
parent <- dirname(getwd())
path <- paste0(parent,"/lcbp/")
datafiles <- list.files(path) %>%
  str_extract(".*\\.Rdata")%>% na.omit %>% paste0(path,.)
for(file in datafiles){
  load(file)
}
#
# processed hobo data
load("C:\\Users\\Admin\\OneDrive - University of Vermont\\LCBP-wetlandP\\Data\\Water\\HOBO\\df.hobo.data_processed_nested.Rdata")
save(df.hobo.data_processed,file="C:\\Users\\Admin\\OneDrive - University of Vermont\\LCBP-wetlandP\\Data\\Water\\HOBO\\df.hobo.data_processed.Rdata")
```

|variable | description |units |
|---------|------------------------|-----|
|datetime | |(yyyy/mm/dd hh:mm:ss)|
|dH       | height of water between sensors as estimated by barometric pressure |(meters) |
|dH_baro_correct | dH corrected for errors in abovewater barometric pressure sensor | (meters) |
|WL_Correction_m | an adjustmet term to get WL referenced to the proper benchmark |(meters) | (meters)|
|WL_rB | water level relative to a benchmark | (meters)|
|Z_bottom | elevation of the channel bottom | meters|
|Z_wl_sensor | elevation of the sensor | meters |


### Water level data at Lewis Creek
```{r}
df.hobo.data_processed_nested %>% filter(site=="LC",plot!="4")

Z_bottom = 112.40 # estimated from 2017 lidar
Z_wl_sensor = 112.51 # estimated from 2017 lidar
H_adjust_m = Z_wl_sensor - Z_bottom

df.LC <- df.hobo.data_processed %>% filter(site=="LC",datetime<"2021-05-15") %>% select(datetime,plot,tempC,dH,dH_baro_correct,WL_Correction_m,WL_rB = WL_rsoil) %>% 
  mutate(dH_baro_temp_correct=ifelse(tempC<2,NA,dH_baro_correct)) %>%
  mutate(WL_rbottom = ifelse(plot=="low",WL_rB + 112.51 - 112.40,WL_rB))

ggplot(df.LC,aes(x=datetime))+
  #geom_line(aes(y=dH))+
  geom_line(aes(y=dH_baro_temp_correct),linetype="dashed")+
  facet_wrap(vars(plot),ncol=1)
```

