---
title: "PrindleBrook_Hydroclimate_Preprocessing"
author: "Adrian Wiegman"
date: "2/5/2021"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message= FALSE)
dependancies <- c("tidyverse",
                  "zoo", # time series functions
                  "broom", # applying functions to nested data
                  "Evapotranspiration", # evapotranspiration modeling
                  "lubridate", # easy date formatting
                  "forecast", # time series functions
                  "cowplot", # to make nice figure pannels
                  "patchwork", # to make nice figure pannels
                  "scales", # to access break formatting functions
                  "akima", # for interpolation of matrixes
                  "rgl",
                  "stringr") # for plotting 3d matrixes
pacman::p_load(dependancies,character.only = T)
```

```{r}
require(stringr)
# Load data
parent <- dirname(getwd())
path <- paste0(parent,"/lcbp/")
datafiles <- list.files(path) %>%
  str_extract(".*\\.Rdata")%>% na.omit %>% paste0(path,.)
for(file in datafiles){
  load(file)
}
#l
```




## Hydroclimatic Variables


The model was forced with precipitation, temperature and wind speed data from Burlington Int'l Airport. Evapotranspiration rate was estimated using the penman monteith method, 

$$

dVw =  A(ip - ET) + Qg + Qin - Qout \\

$$

```{r}
x <- "
Symbol | Units | Definition | Assumptions and Sources
Zs | (m, NAD'83)| elevation of sediment surface  | estimated from LiDAR 0.5m DEM (VCGI), corrected with Emlid Reach RS+ RTK/GNSS survey (centimeter level accuracy) |
Hw | (m) | height of water above sediment surface | measured with HOBO MX2001 water level logger |
Zw | (m, NAD'83)| elevation of water | $Hw +  Zs$ | 
A | (m2) | wetland surface area | interpolated from stage table as $f(Hw)$ |
Vw | (m3) | Water volume of wetland surface water | interpolated from stage table as $f(Hw)$ |
Qin | (m3/day) | Volumetric inflow rate | modeled with HydroCAD and/or solved from water balance |
Qout | (m3/day)| Wetland discharge (outflow) rate | Modeled as a $f(Hw)$ based on site observations | 
ET | (cm/day) | Evapotranspiration rate | Calculated at daily intervals with penman monteith equation via the `Evapotranspiration` package, weather data from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742)  | 
ip | (cm/day) | Precipitation rate | totals derived from sub-hourly weather observations from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742)
Qg | (m3/day) | Groundwater discharge (negative for infiltration) |
Uw |(m/s) | Wind speed | mean derived from sub-hourly data from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742)
Tair | (°C) | Daily air temperature | mean derived from sub-hourly data BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742)
Twater | (°C) | Daily water temperature | Measured by HOBO MX2001 or PME MiniDOT or using equation $5+0.75*Tair$ | 
"
read_delim(x,delim="|") %>% knitr::kable(caption="Table 1. Hydroclimate variables")
```


### Bathymetry and Flow

This table gives the relationships between stage, area, volume and outflow which are based on a HydroCAD model for the catchment. 
```{r}
m.ft = 0.3048 #m/ft 1 foot = 0.3048 m3
m3.acft = 1233.48185532  #ac-ft/m3, 1 acre-foot = 1233.48185532 m3
m3s.cfs = 0.028316847 # 1 cfs = .028 cm/s
cm.in = 2.54 # 1 in = 2.54 cm
HydroCADpath <- "HydroCAD/HydroCAD_model_run1_5and1yr/"
d <- read_csv(paste0(HydroCADpath,"Stage-Area-Storage Table.csv")) %>% left_join(read_csv(paste0(HydroCADpath,"Stage-Discharge Table.csv")))
d <- readxl::read_xlsx("C:/Workspace/wetlandP/data/modeling_inputs/DEMHF_0p7m_PrindleRd_StorageCapacity_TableToExcel.xlsx")
#colnames(d) <- c("Elev.ft","Storage.acft","Discharge.cfs")
Zbottom = d$`Elevation\n(feet)`[1]*m.ft
df.stage_volume_discharge <- d %>% 
  select(Zw=ELEVATION,
         Vw=VOLUME,
         A=AREA) %>%
  mutate(Hw=Zw-112.5) # water height above wl recorder

df.stage_volume_discharge %>% print
x <- "
# Dummy Data
# Water Elevation (m) | Height (m) | Area (m2) | Water Volume (m3) | Outflow (m3/d)
Zw|Hw|A|Vw|Qout
108+0.01|0.01|0.0001|0.00
108+0.015|0.015|158.15|1.58|0.00
108+0.02|0.02|316.31|6.33|0.00
108+0.03|0.03|474.46|14.23|0.00
108+0.04|0.04|632.61|25.30|0.00
108+0.05|0.05|790.76|39.54|0.00
108+0.06|0.06|948.92|56.94|0.00
108+0.07|0.07|1107.07|77.49|0.00
108+0.08|0.08|1265.22|101.22|0.00
108+0.09|0.09|1423.38|128.10|0.00
108+0.10|0.10|1581.53|158.15|0.00
"
plot(df.stage_volume_discharge %>% select(-Zw), main="bathymetric relationships")
save(df.stage_volume_discharge,file="df.stage_volume_discharge.Rdata")
write_csv(df.stage_volume_discharge,"df.stage_volume_discharge.csv")
```

### Climate 

Temperature, Precipitation, Wind Speed Data 


```{r}
load("df.climate.day.Rdata")
df.hydroclimate.day <- df.climate.day %>% 
  filter(city=="Burlington") %>%
  #filter(date>=startdate) %>%
  mutate(days_elapsed = difftime(date,ymd("2019-01-01"),units="days"),
         Uw = DailyAverageWindSpeed*0.44704,
         ip = DailyPrecipitation*2.54,
         Tair = (DailyAverageDryBulbTemperature - 32)/1.8,
         Tair_max = (DailyMaximumDryBulbTemperature - 32)/1.8,
         Tair_min = (DailyMinimumDryBulbTemperature - 32)/1.8,
         Twater = 2.5+0.8*Tair,
         Twater = ifelse(Twater<1,1,Twater),
         ip = ifelse(is.na(ip),0,ip),
         amc = ifelse(is.na(AMC),2,AMC)) %>%
  group_by(date,days_elapsed) %>% 
  select(Uw,ip,Tair,Twater,amc)

load("df.ET.PM.Rdata") 
df.ET.daily <- df.ET.PM$ET.Daily %>% fortify.zoo() %>% rename(date="Index",ET=".") %>%
  mutate(ET=ET/10) # cm/day 

df.hydroclimate.day <- df.hydroclimate.day %>%
  left_join(df.ET.daily)

save(df.hydroclimate.day,file="df.hydroclimate.day.LC.Rdata")
write_csv(df.hydroclimate.day,"df.hydroclimate.day.LC.csv")

df.hydroclimate.day %>% ggplot() +
  geom_line(aes(x=date,y=ip),color="blue",alpha=0.5) +
  geom_line(aes(x=date,y=ET),color="red") + geom_smooth(aes(x=date,y=ET),color="red",span=.2) +
  geom_smooth(aes(x=date,y=ip),color="blue",span=.2)

df.hydroclimate.day %>% ggplot() + geom_line(aes(x=date,y=log(ET)),color="red") +
  geom_smooth(aes(x=date,y=log(ET)),color="red",span=.2)+
  geom_line(aes(x=date,y=log(ip)),color="blue") +
  geom_smooth(aes(x=date,y=log(ip)),color="blue",span=.2)
```

```{r}
load("df.climate.hour.Rdata")
str(df.climate.hour)
df.hydroclimate.hour <- df.climate.hour %>% 
  #filter(city=="Burlington") %>%
  #filter(date>=startdate) %>%
  mutate(days_elapsed = difftime(datetime,ymd_hms("2019-01-01 00:00:00",tz="EST"),units="days"),
         hours_elapsed = difftime(datetime,ymd_hms("2019-01-01 00:00:00",tz="EST"),units="hours"),
         Uw = HourlyWindSpeed*0.44704,
         ip = HourlyPrecipitation*2.54, #inch  to m
         Tair = (HourlyDryBulbTemperature - 32)/1.8,
         Twater = 2.5+0.8*Tair,
         Twater = ifelse(Twater<1,1,Twater),
         ip = ifelse(is.na(ip),0,ip),
         amc = ifelse(is.na(AMC),2,AMC)) %>%
  group_by(date,days_elapsed,datetime,hours_elapsed) %>% 
  select(city,Uw,ip,Tair,Twater,amc)
df.hydroclimate <- df.hydroclimate.hour %>% 
  summary(df.hydroclimate)

df.hydroclimate.hour %>% filter(date>"2019-10-01"&date<"2019-11-15") %>%
  ungroup() %>% 
  select(city,datetime,date,precip_inches=ip,Tair)%>%
  mutate(precip_inches=precip_inches/2.54) %>% 
  write_csv(path="df.climate.subdaily.csv")

# load evapotranspiration data 
load("df.ET.PM.Rdata") 
df.ET.hourly <- df.ET.PM$ET.Daily %>% fortify.zoo() %>% rename(date="Index",ET=".") %>%
  mutate(ET=ET/10/24) # mm/day to m/hr 

df.hydroclimate.hour <- df.hydroclimate.hour %>%
  left_join(df.ET.hourly)

df.hydroclimate.hour  %>% ggplot() + geom_line(aes(x=datetime,y=log(ET)),color="red") +
  geom_smooth(aes(x=datetime,y=log(ET)),color="red",span=.2)+
  geom_line(aes(x=datetime,y=log(ip)),color="blue") +
  geom_smooth(aes(x=datetime,y=log(ip)),color="blue",span=.2)
```


### Water level data

```{r bathymetry}
# FORCING FUNCTIONS
fn.Vw.Hw <- approxfun(x=df.stage_volume_discharge$Hw,
                      y=df.stage_volume_discharge$Vw,
                      rule=2) # Height to Volume
fn.Hw.Vw <- approxfun(x=df.stage_volume_discharge$Vw,
                      y=df.stage_volume_discharge$Hw,
                      rule=2) # Volume to Height
fn.A.Hw <- approxfun(df.stage_volume_discharge$Hw,
                     df.stage_volume_discharge$A,
                     rule=2) # Height to Area
# fn.Qout.Hw <- approxfun(df.stage_volume_discharge$Hw,
#                         df.stage_volume_discharge$Qout*60*60*24,
#                         rule=2) # Height to Outflow (m3d)
```



```{r}
df.hc.unit.long <- df.hc.unit %>% ungroup %>% select(t,-date,-days_elapsed,is.numeric) %>% pivot_longer(cols=c(-t))
df.hc.unit.long %>% ggplot() + geom_line(aes(x=t,y=value)) + facet_wrap(vars(name),scales="free")
gVw <- ggplot(data=df.hc.unit)+geom_line(aes(x=date,y=Vw))
gdVw <- ggplot(data=df.hc.unit)+geom_line(aes(x=date,y=dVw))
gQout <- ggplot(data=df.hc.unit)+geom_line(aes(x=date,y=Qout))
gQin <- ggplot(data=df.hc.unit)+geom_line(aes(x=date,y=Qin))
df.dH.day$Vw_check == 0
```

#### Join Water level data with Hydroclimate data

```{r}
df.hc <- df.hydroclimate.day %>%
  left_join(df.dH.day) %>%
  na.omit() %>%
  mutate(Vw=fn.Vw.Hw(Hw),
         Qout=fn.Qout.Hw(Hw),
         A=fn.A.Hw(Hw),
         Qip = A*ip,
         QET = A*ET)

df.hc <- df.hydroclimate.day %>%
  left_join(df.dH.day) %>%
  na.omit() %>%
  mutate(Vw=fn.Vw.Hw(Hw),
         Qout=fn.Qout.Hw(Hw),
         A=fn.A.Hw(Hw),
         Qip = A*ip,
         QET = A*ET)
df.hc %>% filter(Tair>0) %>% lm(Tw~Tair,data=.) %>% summary
df.hc$Twater = 2.72+.75*df.hc$Tair # linear regresion
df.hc$Twater = ifelse(df.hc$Tair<0,2,df.hc$Twater) # correct for negative values
#df.hc$Twater = 3.5+0.75*Tair # fit by hand regression
ggplot(df.hc) +
  geom_point(aes(y=Tw,x=Tair)) +
  geom_smooth(aes(y=Tw,x=Tair),method="lm")+
  geom_abline(slope=1)
ggplot(df.hc) +
  geom_point(aes(y=Twater,x=Tw)) +
  geom_smooth(aes(y=Twater,x=Tw),method="lm")+
  geom_abline(slope=1)

gT <- ggplot(df.hc) + geom_line(aes(x=date,y=Tw))
gip <- ggplot(df.hc) + geom_line(aes(x=date,y=Qip))
gET <- ggplot(df.hc) + geom_line(aes(x=date,y=QET))
gH <- ggplot(df.hc) + geom_line(aes(x=date,y=Hw))
gQ <- ggplot(df.hc) + geom_line(aes(x=date,y=Qout))
gV <- ggplot(df.hc) + geom_line(aes(x=date,y=Vw))
gA <- ggplot(df.hc) + geom_line(aes(x=date,y=A))
gip/gET/gQ


```


### Inflow Hydrograph from Precipitation Data & 

Here I generate an inflow hydrograph summing precipitation event hydrographs for the model simulation period.

#### 1. Flow vs Time Since Event various event sizes

Load the data from HydroCAD outputs

```{}
AMCs = paste("AMC",1:4) # antecedent moisture condition 1 = dry, 2 = normal, 3 = wet, 4 = saturated/frozen
AMCs = AMCs[2:3] # antecedent moisture condition
sizes = c(199,250) # precipitation over 24hrs in hundredths of an inch
nsizes = length(sizes)
nAMCs = length(AMCs)
# times by sizes matrix for flow 
hydrographs <- vector("list",nsizes*nAMCs)
i=0
j = 1
for (amc in AMCs){
  j = j+1
  print(amc)
  for (size in sizes){
    i = i + 1
    filename <- paste0(HydroCADpath,paste("PrindleBrook Pond 24hr",size,amc,"Hydrograph Table.csv"))
    d <- read_csv(filename) %>% mutate(AMC=amc,size=size) %>% group_by(AMC,size)
    hydrographs[[i]] <- d 
  }
}
df.hydrographs <- reduce(hydrographs,full_join) %>% mutate(Qin = `Inflow\n(cfs)`*m3s.cfs) # units: m3/s 
df.hydrographs.wide <- df.hydrographs %>% 
  pivot_wider(
    id_col=c(`Time\n(hours)`,AMC),
    names_from= c(size),
    values_from=Qin) %>%
  mutate(days_elapsed = ceiling(4*`Time\n(hours)`/24)/4) %>% # break the day into quarters
  select(-`Time\n(hours)`) %>% 
  group_by(days_elapsed,AMC) %>%
  # delete this chunk when all precipitation sizes are available from hydrocad
  mutate(`0`=`199`*0,
         `50`=`199`*.5/2,
         `100`=`199`*1.0/2,
         `150`=`199`*1.5/2,
         `300`=`250`*3/2.5,
         `350`=`250`*1.5/2.5) %>%
  summarize_all(~mean(.*60*60*24))%>% # convert from m3s to m3d
  select(order(colnames(.) %>% na.omit %>% as.numeric)) %>%
  relocate(where(is.numeric), .after = where(is.character)) %>%
  relocate(last_col(), .after = AMC)
```

Delete this chunk when all four AMCs are available from hydrocad
```{}
df.hydrographs.wide2 <- df.hydrographs.wide %>%
  mutate(AMC = ifelse(AMC=="AMC 2","AMC 1","AMC 4")) %>%
  mutate_at(vars(-days_elapsed,-AMC),~case_when(
    AMC=="AMC 4"~.*1.1,
    AMC=="AMC 1"~.*0.25,
    T~.))
  
df.hydrographs.wide <- reduce(list(df.hydrographs.wide,df.hydrographs.wide2),full_join)
```

```{}
. <- df.hydrographs.wide %>% filter(AMC==amc)
times <- .$days_elapsed
sizes <- colnames(.) %>% str_extract("[:digit:]+") %>% na.omit %>% as.numeric
sizes <- sizes*cm.in
AMCs = unique(df.hydrographs.wide$AMC)
nAMCs = length(AMCs)
flow <- vector("list",length = nAMCs)
names(flow) <- AMCs
str(flow)
for (amc in AMCs){
  
  print(amc)
  d <- df.hydrographs.wide %>% filter(str_detect(AMC,amc))
  print(d)
  m <- matrix(data=as.matrix(d[,3:length(d)]),
              nrow=nrow(d),
              ncol=length(sizes),
              dimnames=list(time=d$days_elapsed,
                            size=sizes))
  print(m)
  flow[[amc]] <- m
}
str(flow$`AMC 2`)
```


This table will be generated from HydroCAD, for now I am generating a dummy dataset.

```{}
# Generating dummy data
times <- seq(1,10) # rows
sizes <- seq(0.1,10,length.out=10) #cols
fnAMC <- function(s,t,amc){
  k=1
  if(amc==1){k=2} 
  if(amc==2){k=1.5}
  if(amc==3){k=1.2}
  if(amc==4){k=1.1}
  s*exp(t*-k)+s/1000
}

# times by sizes matrix for flow 
m <- matrix(nrow=length(times),
               ncol=length(sizes),
               dimnames=list(time=times,
                             size=sizes))
flow <- vector("list",4)
for (amc in 1:4){
  flow[[amc]] <- m
  for(i in seq(1,nrow(m))){
    for (j in seq(1,ncol(m))){
      t = times[i]
      s = sizes[j]
      # calculate flow function of s and t
      # and on 3 different AMC classes
      flow[[amc]][i,j] = fnAMC(s,t,amc) 
    }
  }
}

head(flow[[3]])
#print(flow)
#length(flow)
```

Use Akima's method to interpolate the data table 
```{}
require(akima)
  # plot the interpolated surface grid
require(rgl)
showplot=T
if(showplot){
open3d()
bg3d("white") # background
# set parameters
x=times; y=sizes; xlim = c(min(x),max(x)); ylim = c(min(y),max(y)); k_x = 10; k_y = 10
colamc <- c("red","yellow","green","blue")
names(colamc) <- AMCs

# call bicubic.grid
flow.bicubic <- vector("list",length(AMCs))
names(flow.bicubic) <- AMCs
i = 0
for (amc in AMCs){
  i = i + 1
  z=flow[[amc]]
  flow.bicubic[[amc]] <- bicubic.grid(x=x,y=y,z=z,xlim=xlim,ylim=ylim,
                             nx=length(x)*k_x,
                             ny=length(y)*k_y)
  # REPLACE NEGATIVE VALUES WITH ZEROS
  flow.bicubic[[amc]]$z <- flow.bicubic[[amc]]$z %>% 
    apply(c(1,2), function(x) {ifelse(x<0, 0, x)})
  
  if (i == 1){
    persp3d(flow.bicubic[[amc]]$x,
        flow.bicubic[[amc]]$y,
        flow.bicubic[[amc]]$z,
        aspect = c(1, 1, 0.5), alpha=0.5,
        xlab ="time (days)", ylab = "precip (in/day)", zlab = "flow",
        polygon_offset = 1)
  }

  persp3d(flow.bicubic[[amc]]$x,
        flow.bicubic[[amc]]$y,
        flow.bicubic[[amc]]$z,
        front = "lines", back = "lines",
        lit = FALSE, add = TRUE,col=colamc[amc])
}
}

```

#### Matrix of Model Time and Time Since Event Root

Aggregate data on a six hour basis by rounding to the nearest quarter day. 

```{}
require(tidyr)
ndays = 180
startdate = "2019-04-01"
enddate = date(startdate) + days(ndays) - 1
df.hc6hr <- df.hydroclimate.hour %>% 
  filter(date >= startdate & date <= enddate) %>%
  mutate(
    days_elapsed = as.numeric(ceiling(4*days_elapsed) / 4)
  ) %>% 
  group_by(date,days_elapsed)
df.hc6hr.sum <- df.hc6hr %>%
  summarize_at(vars(ip),~sum(.))
df.hc6hr.mean <- df.hc6hr %>%
  summarize_at(vars(Twater,Tair,amc,Uw,ET),~mean(.)) %>%
  mutate(
    ET = ET*6 # cm/hr to cm/6hr
  )
df.hc <- reduce(list(df.hc6hr.sum,df.hc6hr.mean),full_join) 
increments = df.hc$days_elapsed
precip = df.hc$ip
m <- matrix(data=0,
            nrow=nrow(df.hc),
            ncol=nrow(df.hc),
            dimnames=list(start_time=increments,
                          future_time=increments))
str(m)
```


```{}
# start day loop
for(i in seq_along(increments)){ 
  #print(c("i:",i))
  # future day loop
  ts = df.hc$days_elapsed[i] # start time
  ip = df.hc$ip[i]
  amc = paste("AMC",df.hc$amc[i])
  for(j in seq_along (increments)){
    #print(c("j:",j))
    ft = increments[j] # future time 
    dt = ft - ts #difference between future time and start time
    if(dt<=0) next
    z = flow[[amc]]
    m[i,j] = bicubic(x=times,y=sizes,z=z,x0=dt,y0=ip)$z %>% ifelse(.<0,0,.)
  }
}
#View(m)
inflow = colSums(m) 

df.hc$Qin = inflow
save(df.hc, file="df.hc.Rdata")
df.hc %>% ggplot(aes(x=days_elapsed))+geom_col(aes(y=Qin))+ylab("inflow rate (m3d)")
```


```{r}
sub_hydrology_preprocessing <- expression({
  sp <- paste0(s,".",p)
  tau = 1e2
  Z_a <- df.hobo.wetland_summary$elevation[df.hobo.wetland_summary$site_plot==sp]
  df.H <- df.hobo.wetland %>% 
    filter(site==s) %>%
    mutate(date=date(datetime),
         Tw = tempC, 
         Hw = Zw - Z_a) %>% # elevation at plot zero
  na.omit

  # calculate change in height. 
  df.dH <- df.H %>%
    mutate(t = difftime(datetime,ymd_hms("2019-01-01 00:00:00",tz="UTC"),units="days"),
         dHw = c(rep(NA,1),diff(Hw,lag=1)),
         dt = c(rep(NA,1),diff(t,lag=1)),
         dHw_dt = dHw/dt) %>%
    na.omit


  df.H.day <- df.H %>% 
    mutate(date=date(datetime)) %>% 
    group_by(date) %>% 
    summarise(Hw=max(Hw),
            TW=mean(Tw))
  df.dH.day <- df.H.day %>% 
    mutate(t = difftime(date,date("2019-01-01"),units="days"),
         site_plot = sp,
         Z_a=Z_a,
         A = 1,
         dHw = c(rep(NA,1),diff(Hw,lag=1)),
         Vw = Hw*A,
         dt = c(rep(NA,1),diff(t,lag=1))) %>%
  na.omit()

  df.hc.unit <- df.hydroclimate.day %>%
    left_join(df.dH.day) %>%
    mutate(
      Qprecip = A*ip/100, # precipitation,
      QET = A*ET/100, #evapotranspiration,
      Vw = Hw*A*porosity, # water volume
      dVw = dHw*A*porosity,
      Qground = 0,
      Qnet = A*(porosity*dHw - (ip - ET)/100),
      Qout = ifelse(Qnet<0,Qnet+Vw/tau,Vw/tau)*dt,
      Qin = ifelse(Qnet>=0,Qnet+Vw/tau,Vw/tau)*dt) %>%
    na.omit
  df.hc.unit$t = df.hc.unit$days_elapsed - df.hc.unit$days_elapsed[1]
  eval(run)
df.hc <- right_join(df.hc.unit %>% mutate(t=as.numeric(t)),df.hc.model) %>% mutate(jday = yday(date)) %>% na.omit
write_csv(df.hc,paste0("df.hydroclimate.1m.",sp,".csv"))
save(df.hc,file=paste0("df.hydroclimate.1m.",sp,".Rdata"))
write_csv(df.hc.model,paste0("df.hc.model.1m.",sp,".csv"))
save(df.hc.model,file=paste0("df.hc.model.1m.",sp,".Rdata"))
}) # end subroutine
```

```{r}
#rm(list = ls())
#(tidyverse)

init <- expression({
  t = 0
  dt = 1 # time step in days
  nsteps = nrow(df.hc.unit)/dt
  ndays = nrow(df.hc.unit)
  iters = 1:nsteps
  A=1
  HRT = 1
  porosity = 1
  Qg=0

  
  df.hc.model <- data.frame(t=rep(NA,nsteps),
                          ip=rep(NA,nsteps),
                          ET=rep(NA,nsteps),
                          Qg=rep(NA,nsteps),
                          Qin=rep(NA,nsteps),
                          Qout=rep(NA,nsteps),
                          dVw=rep(NA,nsteps),
                          Vw=rep(NA,nsteps),
                          Hw=rep(NA,nsteps))
  # FORCING FUNCTIONS
  f.ET <- approxfun(df.hc.unit$t,df.hc.unit$ET)
  f.ip <- approxfun(df.hc.unit$t,df.hc.unit$ip)
  f.dHw <- approxfun(df.hc.unit$t,df.hc.unit$dHw)
  f.Hw <- approxfun(df.hc.unit$t,df.hc.unit$Hw)
})

odes <- expression({
  if(i == ndays) break()
  t = t + dt # move time foreword
  ip = f.ip(t)*dt # precipitation
  ET = f.ET(t)*dt #evapotranspiration
  Hw = f.Hw(t) # water depth
  Vw = Hw*A*porosity # water volume
  dHw =f.dHw(t)*dt # change in depth
  dVw = dHw*A*porosity
  Qnet = A*(porosity*dHw - (ip - ET)/100)
  Qout = ifelse(Qnet<0,Qnet+Vw/HRT,Vw/HRT)*dt
  Qin = ifelse(Qnet>=0,Qnet+Vw/HRT,Vw/HRT)*dt
  #cat("\ni=",i," t=",t," dVw (m3)=",dVw)
  if(Vw < 0){
     Qout = Qout + dVw
     dVw = 0
     Vw = 0
  }

  #cat("\ni=",i," dVw (m3)=",dVw)
  # save outputs in dataframe 
  df.hc.model$t[i]=t
  df.hc.model$Qg[i]=Qg
  df.hc.model$Qin[i]=Qin
  df.hc.model$Qout[i]=Qout
  df.hc.model$dVw[i]=dVw
  df.hc.model$Hw[i]=Hw
  df.hc.model$ip[i]=ip
  df.hc.model$ET[i]=ET
  df.hc.model$Vw[i]=Vw
})

run <- expression({
  eval(init)
  for (i in iters){
    eval(odes)
    }
  })
```

```{r area 1m}
#load("C:\\Workspace\\wetlandP\\data\\lcbp\\hifreq.Rdata")
sites <- c("LC","OCD","OCSP")
plots <- 0:4
p <- 0
s <-  "OCD"
for(s in sites){
  for(p in plots){
  eval(sub_hydrology_preprocessing)
  }}
```

Calculate Storage Based on Water balance


```
library(dplyr)
df.obspred <- inner_join(df.hc.unit %>% ungroup %>% mutate(t=as.double(t)) %>% select(t,Vw,Hw),
                         df.hc.model %>% select(t,Vw_pr=Vw,Hw_pr=Hw))

df.hc.model.long <- df.hc.model %>% group_by(t) %>% pivot_longer(cols=c(-t))
df.hc.model.long %>% ggplot() + geom_line(aes(x=t,y=value)) + facet_wrap(vars(name),scales="free")
View(df.obspred)
df.obspred %>% ggplot() + geom_line(aes(x=t,y=Vw))+geom_line(aes(x=t,y=Vw_pr),color="red",linetype="dashed")
lm(Vw_pr~Vw,data=df.obspred) %>% summary
```
