---
title: Documentation -- `r {require(tidyverse);mv = stringr::str_extract(getwd(),'[^/]+$');
  mv}`
author: "Adrian Wiegman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

**Note this project is still under development**

## About

The `r mv` model is an ordinary differential equation model developed for decadal phosphorus (P) retention simulations in riparian wetlands with a range of soil and hydrologic conditions. 

### Funding

**Quantifying phosphorus retention in restored riparian wetlands of the Lake Champlain Basin**

EPA Grant: LC00A00394

Job Cost Code: 995-002-001

#### Project Team:

  Eric D. Roy, Ph.D., University of Vermont (Principle Investigator)

  Breck Bowden, Ph.D., University of Vermont (Investigator)

  Kristin Underwood, Ph.D., University of Vermont (Investigator)

  Adrian Wiegman, M.S., University of Vermont (PhD Candidate)

#### Granting Agency:

  Lake Champlain Basin Program

  54 West Shore Road

  Grand Isle, VT 05458

### Buildnotes

Model version: `r mv`

The data for this project are hosted at the authors private github repository:
https://github.com/arhwiegman/wetlandP

The current version of the model is available within the wetlandP repository: https://github.com/arhwiegman/wetlandP/tree/master/model_versions/wetlandP_v2/wetlandP_v2.1

This repository will be made public upon publication of this work. 

#### Status (of this version)

1. Switches have been added to toggle process flow rates see `IO_` in parameters. 
2. All hydroclimatic variabels are read in as input data then fit to an `approxfun` so that values can be interpolated at any discrete time point. See `scripts/preprocssing` for preparation of hydroclimatic input table.  
3. Moved away from the use of langmuir model of adsorption, instead DIP_E can either be entered as a constant, or calculated using a power model fit to final intact core SRP and (Ex_max - Ex)/(PSR). 
3. New script added to keep track of and, when needed, install dependancies.
4. `Packrat` is no longer being used `pacman` is being used to install load packages. 
5. Revised biomass growth equations to include temperature effects on growth rate and mortality, and omit water level and self crowding effects on growth rate. 

#### Potential Next steps (for future versions)

1. Incorporate subroutine that takes raw climate data from weather stations and water level data and prepares a proper input table. 
2. Add subroutines for P flows due to periphyton, bioturbation
3. Add subroutine to toggle aerobic/anearobic sediments and associated changes in DIP_E
3. Improve computational efficiency (decrease simulation time).
4. Add option to use NRCS Soil Survey Data and/or Farming Frequency and/or Years since farming to initialize state variables. 
5. Add the ability to take hydrologic parameters such as inundation frequency and depth, and produce a synthetic flood hydrograph. 
6. Add subroutines for management including: fertilizer additon, biomass harvest, ditch plugging, and berm removal
7. Implement the `r mv` R project with `packrat` to avoid compatability issues among local R package versions (Ushey et al. 2018).
8. Add subroutines for freeze/thaw

## Getting Started

The `r mv` model is written in R version 4.0.1 (2020-06-06) -- "See Things Now" using Rstudio (v. 1.2.1). An R project file (.Rpoj) is the user interface.To run the model, click on the `r dir()[str_detect(dir(),".Rproj")]` file. This will open up Rstudio with the `r mv` working directory.

### Running the Model

Read the remainder of this section for details on how to edit parameters and run the model and view model outputs. 

### File Structure

A current list of the working directory is given below. 
```{r}
dir()
```
The sections below describe the `documentation`, `scripts`,  `inputs`, and `outputs` in more detail.

### Dependacies

A script called `dependancies.R` uses `pacman` to check for and install required R packages. The `r mv` simulations are implemented with the `deSolve` package (Soetaert et al. 2010), data management and plotting is implemented with the `tidyverse` packages (Wickham et al. 2019). For more details on the packages used see the `scripts/dependancies.R` file.

Upon running this file you will see the following console output
```{r}
source(file.path(getwd(),"scripts","dependancies.R"))
```

The `dependancies.R` script also creates an object called depedancy_citations. You can `print` this and copy it to add the package citations to a bibliography. 

### Documentation Folder

Currently the most detailed documentation of the model is within the model scripts. However this folder contains tables that document model variables, values, assumptions, etc... for major varaible types in the model. 

```{r}
dir("documentation")
```

### Scripts Folder

```{r}
dir(file.path(getwd(),"scripts"))
```
In addition to the files above the scripts folder holds four folders. `_implementations` contains high level scripts used to call the model and edit inputs and outputs. `_preprocessing` contains scripts to conduct statistical analysis to general parameter estimates or to calculate the hydroclimate forcing tables. `_postprocessing` contains scripts to analyze model outputs. `_sourcecodes` contains copies of the model source codes in the main `scripts` folder. These are kept in case the user makes manual edits to the source codes that cause errors.

The table below provides a description of each of the source codes used by the model.

| name | description |
| --- | --- |
| `xecute.R` | High level script to load source code, execute simulation and manage data  outputs. This script must be run to implement the model. To run the file: in `Rstudio` with the `xecute.R` file open press `cmd/crtl + shift + enter` |
| `parameters.R` | The main way to manipulate outputs. This includes both nurmerical constants to be used in model calculations as well as model run specifications (e.g. static or dynamic, simulation time) see `fn_edit_parameter_values` to change individual parameters for before  a given run. |
| `model.R` | Contains the high level functions that controling flow of subroutines in the `r mv` model. See subroutines for details of model calculations.|
| `initialize.R` | initializes the model state variables based on the parameter values and functions provided. |
| `subroutines.R` | a series of subroutines that calculate new values of variables in the model based on functions, parameters and variable values in the model environment. |
| `functions.R` | a high level script that sources other functions. |
| `functions/fns_X.R` | functions pertaining to `X` aspect of the model (such as "processes") |
| `dependancies.R` | checks for and installs required R packages |

### Inputs Folder

Inputs are taken as `.csv` (comma separated values) files and read in using the function `readr::read_csv()`. There are two kinds of input file, `df.hydroclimate...csv` and `df.parameters...csv`.`hydroclimate` files provide a time series of forcing data with the top row as the variable name and each column containing the values for the variable at time `t`, at least one column must be named `t`. `parameters` files are tables with the columns from left to right variable name, default value, units, description, assumptioms, random distribution function name and inputs. 

```{r}
dir("inputs")
```

### Outputs Folder

The model saves outputs with a prefix then the simulation then a timestamp. `r mv` produces three types of output: 

| prefix | extension | description | 
|---|---|---|
| `sim_` | `.Rdata` | an image of the R environment objects saved upon execution of the model run. Use `load("sim_[run name].Rdata")` in R to load the environment objects for the simulation. |
| `fig_` | `.png` | time series plots of variables |
| `outputs_`| `.csv` | a comma delimited data table of variable values along the time series the model run | 

A snapshot of the outputs folder is given below:
```{r}
head(dir("outputs"))
```

## Model Variables

```{r, include=FALSE}
diagram_path <- paste0(getwd(),"/documentation/wetlandP_v2.1_Conceptual_Diagram.png")
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
source("documentation/generate_documentation_tables.R")
```

This section contains summary tables defining the major variables of `r mv`. A conceptual diagram of model domain, compartments, state variables, and processes is given below. Flows of phosphorus are represented by lines with arrows, the associated process for each flow is labeled in italics. State variables are represented in boxes with rounded edges. See the sections below for detailed definitions of states, processes, etc.

![](`r diagram_path`)

The figure below shows a time series plot of the model state variables. 

```{r, fig.fullwidth=TRUE}
load("C:\\Workspace\\wetlandP\\model_versions\\wetlandP_v1\\wetlandP_v1.1\\outputs\\sim_static_Z_w_2020-05-18_May051589821296.Rdata")
print(figs$states)
```

The default parameters for `r mv` currently produce state variable values close to what has been observed in the field. This includes dissolved inorganic P concentrations (see plot below)

```{r }
print(fig_DIP)
```


### State variables
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "states",
                   range = "B2:D16")
knitr::kable(df,
               digits=4,
               cap="state variables calculated with ordinary differential equations",
               format = "pandoc")
```

### Processes 

#### Flows
```{r}
df <- fn_generate_doc_table(fconn="scripts/subroutines.R",
                      startline=591,
                      endline=624,
                      fname="processes")
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")

knitr::kable(df,
             digits=4,
             cap="process flows (adding or subtracting from state variables)",
             format = "pandoc")

```

#### Rates
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "rates",
                   range = "A2:D12")
knitr::kable(df,
             digits=4,
             cap="process rates (calculated as a function of forcing variables, intermediate variables and state variables)",
             format = "pandoc")
```

### Forcings (Hydroclimatic Inputs)

The table below gives the variable names and assumptions for the forcing variables used in the model. The model was forced with water level data collected in situ and meteorological data from Burlington Int'l Airport (NOAA NCDC). Water level was measured at field sites by HOBO MX2001 pressure and temperature sensors placed just below the soil surface. Data was corrected for variation in local barometric pressure, also measured by HOBO MX2001s. Any gaps in the water level sensor record were filled via time lag regression with other sensors in the area or with USGS guages (USGS NWIS, r^2>0.9). Water temperature was modeled from air temperature based using a statistical fit to with miniDOT sensors at the soil water interface (r^2>0.9). Precipitation was taken as the daily totals from meteorological data. Evapotranspiration rate was estimated using the penman monteith method via the R package `evapotranspiration`, substituting sunshine hours for solar radiation. Water volume were calculated from area, porosity (assumed = 1), and water depth. We caclulated the first derivative in the time of water volume, and used this to solve for net surface flow. Surface inflow and outflow were deduced from net surface flow by adjusting for through flow. Through flow was calculated as the volume of water divided by the days hydraulic residence time (HRT or $\tau$). 



$$


\text{HYDROLOGY SUBROUTINE:}\\
V_w = A\rho_aH_w\\
dV_{w} = V_{w,t} - V_{w,t+1} \\
Q_{net}=  dV_w - A(ip - ET) \\
\text{IF Q}_\text{net} > 0: \\ 
Q_{in} = Vw/\tau + Qnet \\
Q_{in} = - V_w/\tau \\
\text{ELSE:} \\
Q_{in} = V_w/\tau \\
Q_{out} = V_w/\tau - Q_{net} \\


$$


```{r}
x <- "
Symbol | Units | Definition | Assumptions and Sources
Zs | (m, NAD'83)| elevation of sediment surface  | estimated from LiDAR 0.5m DEM (VCGI), corrected with Emlid Reach RS+ RTK/GNSS survey (centimeter level accuracy)
Hw | (m) | height of water above sediment surface | measured with HOBO MX2001 water level logger 
Zw | (m, NAD'83)| elevation of water | Hw +  Zs 
A | (m^2) | wetland surface area | interpolated from stage table as f(Hw)
Vw | (m^3) | Water volume of wetland surface water | calculated from A and H_w 
ET | (cm/day) | Evapotranspiration rate | Calculated at daily intervals with penman monteith equation via the `Evapotranspiration` package, weather data from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742) (NOAA NCDC)   
ip | (cm/day) | Precipitation rate | totals derived from sub-hourly weather observations from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742)(NOAA NCDC)
Qnet | (m^3) | net surface flow | deduced from dVw, and A(ip - ET)
Qin | (m^3/day) | Volumetric inflow rate | modeled with HydroCAD and/or solved from water balance 
Qout | (m^3/day)| Wetland discharge (outflow) rate | Modeled as a f(Hw) based on site observations  
Qg | (m^3/day) | Groundwater discharge (negative for infiltration) | assumed = 0
Uw |(m/s) | Wind speed | mean derived from sub-hourly data from BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742) | used in evapotranspiration calculation  
Tair | (°C) | Daily air temperature | mean derived from sub-hourly data BURLINGTON INTERNATIONAL AIRPORT, VT US (WBAN:14742) | 
TW | (°C) | Daily water average temperature | Modeled from Tair using equation from linear model fit to temperature measured with PME miniDOT. IF(Tair > 0): TW = 2.5+0.8Tair ELSE: TW = 0
"
read_delim(x,delim="|") %>% knitr::kable(caption="Table 1. Hydroclimate variables",
             format = "pandoc")
```

### Parameters 

```{r}
df <- fn_generate_doc_table(
  fconn="documentation/parameters_local.R",
  fname="parameters_local",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="local (measured) parameters")

df <- fn_generate_doc_table(
  fconn="documentation/parameters_stochastic.R",
  fname="stochastic",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="stochastic (unmeasured/calibrated) parameters")

df <- fn_generate_doc_table(
  fconn="documentation/parameters_universal_constants.R",
  fname="parameters_universal_constant",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="universal constant parameters")

df <- fn_generate_doc_table(
  fconn="documentation/parameters_simulation.R",
  fname="parameters_simulation",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="run specifications parameters")
```
 
### Differential Equations

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** and **process flows** (see **"mass balance"**).

```{r}
df <- read_lines(as.character(sub_diffeqs)) %>% 
  str_subset("=") %>% 
  str_squish() %>%
  str_split("=",simplify = TRUE)
colnames(df) <- c("Name","Value")
knitr::kable(df,
             format = "pandoc",
             cap="Differential equations for model states")
```
 
### Mass balance

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** (state or states for short) and **process flows** (see `stoicheometry.xlsx`). In this matrix the modeler enters a value of 1 (adding to a state), -1 (subtracting from state) or blank (not interacting with a state) for each combination of a state variable and a process flow. The table below contains the stoicheometry matrix for the current model. Note the column `balance` is the row sum for a given process, values above or below than zero indicates that a process adds/removes mass from the model domain, while a balance of zero indicates that a process is conservative (does not affect the total mass in the domain). 

```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "stoicheometry",
                   range = "B2:P29") 
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="parameters (numeric constants and run specifications)",
             escape=FALSE)
```

### Numerical Stability Checks

The following figures verify the performance of the model under increasing complexity of simulation. 


```{r, echo=FALSE,message=FALSE,results="asis"}
# results="asis" converts text outputs to markdown
fig_path <- paste0(getwd(),"/documentation/")
figs <- dir(fig_path) %>% .[str_detect(.,".*W.*B.*G.*png$")]
captions <- c(
  "1. Water Off, Biology Off, Geochemical Off (States, g P/m2)",
  "2. Water Off, Biology Off, Geochemical On (States, g P/m2)",
  "3. Water Off, Biology On, Geochemical Off (States, g P/m2)",
  "4. Water Off, Biology On, Geochemical On (States, g P/m2)",
  "5. Water On, Biology Off, Geochemical Off (Hydroclimate Static)",
  "6. Water On, Biology Off, Geochemical Off (Hydroclimate Dynamic)",
  "7. Water On, Biology On, Geochemical On (States, g P/m2)",
  "8. Water On, Biology On, Geochemical On (Concentrations)")
captions <- c(
  "1. all stocks should be constant through time",
  "2. DIP and PIP should equilibrate, no other stocks should change",
  "3. shootP, rootP, LOP, ROP should fluctuuate, DIP and PIP should be constant",
  "4. all state variables should fluctuate",
  "5. volume of water should be constant through time",
  "6. hydrocliamte data being forced on the model",
  "7. all states should fluctuate but there should be no discontinuities, or negative values, inorganic matter compartment should be constant since TSS = 0",
  "8. concentrations shoudl fluctuate but have no sharp discontinuities, or negative values")
for (i in seq_along(figs)){
  cat(paste("####",captions[i],"\n\n"))
  cat(paste("\n![",captions[i],"](",file.path(fig_path,figs[i]),")\n\n"))
}
```
 
## References

### Online Data Sources

NOAA NCDC. National Oceanographic and Atmospheric Administration, National Centers for Environmental Information, National Climatic Data Center. United States Department of Commerce. URL: www.noaa.ncdc.gov (accessed on 2021-10-25).


USGS NWIS. United States Geologic Survey, National Water Information System. United States Department of the Interior. URL: www.waterdata.usgs.gov (accessed on 2021-10-25).

VCGI. Vermont Open Geodata Portal, Vermont Center for Geographic Information. AGENCY OF DIGITAL SERVICES. URL: www.geodata.vermont.gov (acessed on 2021-10-25)


### Scientific Literature

DeLaune, R. D., Baumann, R. H., & Gosselink, J. G. (1983). Relationships among Vertical Accretion, Coastal Submergence, and Erosion in a Louisiana Gulf Coast Marsh. SEPM Journal of Sedimentary Research, 53(1), 147–157. https://doi.org/10.1306/212F8175-2B24-11D7-8648000102C1865D

Hantush, M. M., Kalin, L., Isik, S., & Yucekaya, A. (2013). Nutrient Dynamics in Flooded Wetlands. I: Model Development. Journal of Hydrologic Engineering, 18(12), 1709–1723. https://doi.org/10.1061/(ASCE)HE.1943-5584.0000741

Marois, D. E., & Mitsch, W. J. (2016). Modeling phosphorus retention at low concentrations in Florida Everglades mesocosms. Ecological Modelling, 319, 42-62.

Morris, J. T., Houghton, R. A., & Botkin, D. B. (1984). Theoretical limits of belowground production by Spartina alterniflora: An analysis through modelling. Ecological Modelling, 26(3–4), 155–175. https://doi.org/10.1016/0304-3800(84)90068-1

Morris, J. T., & Bowden, W. B. (1986). A Mechanistic, Numerical Model of Sedimentation, Mineralization, and Decomposition for Marsh Sediments1. Soil Science Society of America Journal, 50(1), 96. https://doi.org/10.2136/sssaj1986.03615995005000010019x

Morris, J. T., Sundareshwar, P. V., Nietch, C. T., Kjerfve, B., & Cahoon, D. R. (2002). Responses of coastal wetlands to rising sea level. Ecology, 83(10), 2869-2877.

Morris, J. T., Barber, D. C., Callaway, J. C., Chambers, R., Hagen, S. C., Hopkinson, C. S., … Wigand, C. (2016). Contributions of organic and inorganic matter to sediment volume and accretion in tidal wetlands at steady state. Earth’s Future, 4(4), 110–121. https://doi.org/de

Reddy, K. R., & Delaune, R. D. (2008). Biochemistry of wetland science and application. CRC Press Taylor & Francis Group, Boca Raton FL. ISBN 978-1-56670-678-0

Wang, N., & Mitsch, W. J. (2000). A detailed ecosystem model of phosphorus dynamics in created riparian wetlands. Ecological Modelling, 126(2–3), 101–130. https://doi.org/10.1016/S0304-3800(00)00260-X

Wang, H., Appan, A., & Gulliver, J. S. (2003). Modeling of phosphorus dynamics in aquatic sediments: I - Model development. Water Research. https://doi.org/10.1016/S0043-1354(03)00304-X

Wiegman, A. R. H., Day, J. W., D’Elia, C. F., Rutherford, J. S., Morris, J. T., Roy, E. D., … Snyder, B. F. (2018). Modeling impacts of sea-level rise, oil price, and management strategy on the costs of sustaining Mississippi delta marshes with hydraulic dredging. Science of the Total Environment, 618, 1547–1559. https://doi.org/10.1016/j.scitotenv.2017.09.314


### Software Dependancies 
```{r,results="asis"}
print(dependancy_citations)
```
