---
title: "wetlandP version 1.1 -- Documentation"
author: "Adrian Wiegman"
date: "5/17/2020"
output: 
  html_document:
    toc: TRUE
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## About

### This Project 

**Quantifying phosphorus retention in restored riparian wetlands of the Lake Champlain Basin**

EPA Grant: LC00A00394
Job Cost Code: 995-002-001

Prepared by:
Eric D. Roy, Ph.D., University of Vermont
Breck Bowden, Ph.D., University of Vermont
Kristin Underwood, Ph.D., University of Vermont
Adrian Wiegman, M.S., University of Vermont

Prepared for:
Lake Champlain Basin Program
54 West Shore Road
Grand Isle, VT 05458

### This Folder

This folder contains the wetlandP model (v. 1.1). The model is an ordinary differential equation model implemented in R (v. 4.0.0) and Rstudio (v. 1.2.1) or later. with the `deSolve` (v. 1.28) package (Soetaert et al. 2010). This document gives details on how the folder is organized and how to implement the model. The model relies on the packages within the `tidyverse` (Wickham 2019), for plotting, data manipulation and string editing. 

The development versions of model are hosted on github @ https://github.com/arhwiegman/wetlandP/model_versions/

The stable versions model is also hosted uvm gitlab page.
[insert link]. 

### Buildnotes

wetlandP_v1.1

#### Status (of this version)

1. The subroutines have been checked for mass balance and numerical stability. The model functions when water is above and below the soil surface during static simulations. 
2. Model rate functions have been checked but metadata needs to be updated. 

#### Next steps (for future versions)

1. The model mass balance and stability needs to be verified for dynamic simulations 
2. Subroutines for calibration need to be coded
3. Scenarios need to be coded
4. The model performance needs to be optimized for run speed

## Getting Started

To run the model, click on the `wetlandP_vX.X.Rproj` file. This will open up Rstudio with the working directory set to `wetlandP_vX.X`. 

### File Structure

The working directory contains folders for model `documentation`, `scripts`,  `inputs`, and `outputs`. The `packrat` folder contains libraries for model's dependancies (e.g. `deSolve`). A current list of the working directory is given below. 

```{r}
dir()
```

### Documentation Folder

Currently the most detailed documentation of the model is within the model scripts. Open the [wetlandP_documentation](## Documentation) notebook in your web browser for a summary of the model state variables and the assumptions governing their differential equations.

### Scripts Folder

```{r}
dir("scripts")
```

The table below provides a description of each of the scripts used by the model.

| name | description |
| --- | --- |
| `xecute.R` | Loads source code, executes simulation and manages data  outputs. This script must be run to implement the model. To run the file: in `Rstudio` with the `xecute.R` file open press `cmd/crtl + shift + enter` |
| `parameters.R` | The main way to manipulate outputs. This includes both nurmerical constants to be used in model calculations as well as model run specifications (e.g. static or dynamic, simulation time) see `fn_edit_parameter_values.R` to change individual parameters for before  a given run. |
| `model.R` | The high level script controling flow of subroutines in the wetlandP model. See subroutines for details of model calculations.|
| `initialize.R` | initializes the model state variables based on the parameter values and functions provided. |
| `subroutines.R` | a series of subroutines that calculate new values of variables in the model based on functions, parameters and variable values in the model environment. |
| `functions.R` | a high level script that sources other functions. |
| `fns_X.R` | For detailed functions pertainin to `X` aspect of the model |

### Inputs Folder

Inputs are data that are used to force or calibrate the model. Examples include water level data, weather station data, nutrient concentrations and so on. A calibration subroutine still needs to be added so the inputs folder is currently empty. 

### Outputs Folder

The model saves outputs with a prefix then the simulation then a timestamp. The model produces three types of output: 

| prefix | extension | description | 
|---|---|---|
| "sim_" | ".Rdata" | an image of the R environment objects saved upon execution of the model run. Use `load("sim_[run name].Rdata")` in R to load the environment objects for the simulation. |
| "fig" | ".png" | time series plots of variables |
| `outputs`| ".csv" | a comma delimited data table of variable values along the time series the model run | 

## Model Documenation Tables

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
source("documentation/generate_documentation_tables.R")
```

The figure below shows a plot of the This section contains summary tables documenting the major components of the wetlandP model. *The current model version is 1.1*. 

```{r, fig.fullwidth=TRUE}
load("C:\\Workspace\\wetlandP\\model_versions\\wetlandP_v1\\wetlandP_v1.1\\outputs\\sim_static_Z_w_2020-05-18_May051589815528.Rdata")
print(figs$states)
print(fig_DIP)
```

### State variables
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "states",
                   range = "B2:D16")
knitr::kable(df,
               digits=4,
               cap="state variables calculated with ordinary differential equations",
               format = "pandoc")
```

### Processes 

#### Flows
```{r}
df <- fn_generate_doc_table(fconn="scripts/subroutines.R",
                      startline=408,
                      endline=435,
                      fname="processes")
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")

knitr::kable(df,
             digits=4,
             cap="process flows (adding or subtracting from state variables)",
             format = "pandoc")

```

#### Rates
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "rates",
                   range = "A2:D12")
knitr::kable(df,
             digits=4,
             cap="process rates (calculated as a function of forcing variables, intermediate variables and state variables)",
             format = "pandoc")
```

### Parameters 

```{r}
df <- fn_generate_doc_table(
  fconn="scripts/parameters.R",
  fname="parameters",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="parameters (numeric constants and run specifications)")
```
 
### Differential Equations

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** and **process flows** (see **"mass balance"**).

```{r}
df <- read_lines(as.character(sub_diffeqs)) %>% 
  str_subset("=") %>% 
  str_squish() %>%
  str_split("=",simplify = TRUE)
colnames(df) <- c("Name","Value")
knitr::kable(df,
             format = "pandoc",
             cap="Differential equations for model states")
```
 
### Mass balance

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** (state or states for short) and **process flows** (see `stoicheometry.xlsx`). In this matrix the modeler enters a value of 1 (adding to a state), -1 (subtracting from state) or blank (not interacting with a state) for each combination of a state variable and a process flow. The table below contains the stoicheometry matrix for the current model. Note the column `balance` is the row sum for a given process, values above or below than zero indicates that a process adds/removes mass from the model domain, while a balance of zero indicates that a process is conservative (does not affect the total mass in the domain). 

```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "stoicheometry",
                   range = "B2:P29") 
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="parameters (numeric constants and run specifications)",
             escape=FALSE)
```
 
## References

  Karline Soetaert, Thomas Petzoldt, R. Woodrow Setzer (2010).
  Solving Differential Equations in R: Package deSolve. Journal
  of Statistical Software, 33(9), 1--25. URL
  http://www.jstatsoft.org/v33/i09/ DOI 10.18637/jss.v033.i09
