---
title: "wetlandP documentation"
author: "Adrian Wiegman (adrian.wiegman@uvm.edu)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_notebook
tables: TRUE
figures: TRUE
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
source("documentation/generate_documentation_tables.R")
```

This file contains a summary tables documenting the major components of the wetlandP model. *The current model version is 1.1*. 


## State variables
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "states",
                   range = "B2:D16")
knitr::kable(df,
               digits=4,
               cap="state variables calculated with ordinary differential equations",
               format = "pandoc")
```

## Processes 

### Flows
```{r}
df <- fn_generate_doc_table(fconn="scripts/subroutines.R",
                      startline=408,
                      endline=435,
                      fname="processes")
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")

knitr::kable(df,
             digits=4,
             cap="process flows (adding or subtracting from state variables)",
             format = "pandoc")

```

### Rates
```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "rates",
                   range = "A2:D12")
knitr::kable(df,
             digits=4,
             cap="process rates (calculated as a function of forcing variables, intermediate variables and state variables)",
             format = "pandoc")
```

## Parameters 

```{r}
df <- fn_generate_doc_table(
  fconn="scripts/parameters.R",
  fname="parameters",
  patt = "^[^#]+=.+#.+\\|.+\\|.*$", # string pattern
  startline = 0,
  endline = -1L)
df$Value <- str_replace_all(df$Value,"\\*","\\\\\\*")
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="parameters (numeric constants and run specifications)")
```
 
## Differential Equations

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** and **process flows** (see **"mass balance"**).

```{r}
df <- read_lines(as.character(sub_diffeqs)) %>% 
  str_subset("=") %>% 
  str_squish() %>%
  str_split("=",simplify = TRUE)
colnames(df) <- c("Name","Value")
knitr::kable(df,
             format = "pandoc",
             cap="Differential equations for model states")
```
 
## Mass balance

Differential Equations for the model are generated from stoicheometry matrix of the **state variables** (state or states for short) and **process flows** (see `stoicheometry.xlsx`). In this matrix the modeler enters a value of 1 (adding to a state), -1 (subtracting from state) or blank (not interacting with a state) for each combination of a state variable and a process flow. The table below contains the stoicheometry matrix for the current model. Note the column `balance` is the row sum for a given process, values above or below than zero indicates that a process adds/removes mass from the model domain, while a balance of zero indicates that a process is conservative (does not affect the total mass in the domain). 

```{r}
df <- readxl::read_excel("documentation/stoicheometry.xlsx",
                   "stoicheometry",
                   range = "B2:P29") 
knitr::kable(df,
             digits=4,
             format = "pandoc",
             cap="parameters (numeric constants and run specifications)",
             escape=FALSE)
```
 
