
In this chapter I demonstrate the use of the model for estimating event level P dynamics, using a simple set of inputs. 

Vary the following inputs to the model in a factorial grid or random search. Then search through inputs for high and low P release and P retention. The inputs listed below are non-random site specific things that can be estimated from existing data. 

#Measureable Non-random Site Factors:
```{r}
# Environmental Forcing Factors
df_env_factors <- expand.grid( 
  #Variable = Values # units; description; notes
  Tw= c(2,20), # degC; Temperature of water; AKA biology effects
  Hw = c(0.5), # m; peak flood depth; keep constant for now as fluxes scale with flood depth
  duration = c(2,20), # d; duration of flood event;
  tau = c(0.1,10,20), # d; residence time; affects flow velocity 
  ISS = c(5,50), # mg/l; inorganic suspended sediments; 
  OSS = c(1,5), # mg/l; organic suspended sediments;
  SRP = c(0.005,0.05), # mg/l; the range of what was observed in the river
  ISS2TP_slope = c(0.5e-3,1e-3) # mg/l; 1e-3 is roughly what I observed at otter creek
)
print(df_env_factors)

# SOIL FACTORS
df_soil_factors = expand.grid(
  LOI = c(0.05,0.5), #g/g; Loss-on-igniton; affects bulk density and combines with Fines to affect Smax)
  Fines = c(0.7,0.9), #g/g; fraction of IM as fines (silt+clay); combines with LOI to affect Smax
  PSR = c(0.05,0.5) #mol/mol; molar ratio of oxalate P to the sum of Al and Fe, combines with LOI and fines to affect, exchangeable IP pool)
  )

df_merged_factors <- merge(df_soil_factors,df_env_factors)
str(df_merged_factors)
est_run_time_sec= 1
print(paste("Est. run time is",signif(nrow(df_merged_factors)*est_run_time_sec/60/60,3),"hours"))
```

#Map Variables to Model Add Model Outputs to Dataframe
```{r}
```

#Calculate Summary Statistic For Model
```{r}
```

#Plot Results
```{r}
```